\noindent
\textbf{Expected Feedback and Discussion Points:}
\begin{itemize}
    \item Does \myname's idea generalize beyond precision agriculture, e.g., precision livestock management, smart storage, smart homes?
    \item Can the resourceful devices capable of running AL/ML tasks at the mid-tier fully remove the cloud dependency?
    \item Are there precision agriculture applications that cannot be deployed using \myname{}?
\end{itemize}

\noindent
\textbf{Controversial Points, and Open Issues:}
\begin{itemize}
    \item \myname offers the flexibility to deploy any precision agriculture application that can be supported by the available hardware. However, configuring and deployment these applications can be a challenging task for the farmers and academics who are not familiar with the technology. A carefully designed UI is very important to ensure good user experience. 
    \item There is an interoperability and integration challenge with the \myname. Ideally, it should allow the users to integrate their existing IoT solutions with the \myname. However, there are open questions in this regard. For example, what kind of IoT devices and platforms can integrate? At what tier of the architecture the integration happens? 
\end{itemize}

\noindent
\textbf{When Does the Idea Fall Apart:}
\begin{itemize}
    \item The users will lose access to the most recent data if there is no internet connectivity for long periods. However, the data will still be stored at the mid-tier devices and uploaded to the top-tier when the internet connectivity is available. 
\end{itemize}